---
title: "ANA515- Assignment 2 - Week  4"
author: "Sandeep Tom"
date: "11/14/2021"
output:
  word_document: default
---
#Section 1: Description of the data.
The data we are using are temperature measurements that were taken across different cities in the United stats over the course of a 12-month period June 2014 to June 2015. The data taken across multiple cities tells us what the year looked like with record setting temperatures. The data used here is the for the city of Philadelphia.

 
```{r, include=FALSE}
#Reading the Data from the URL provided in the github document
library(tidyverse)
library(readr)
library(knitr)
library(bslib)
library(dplyr)
library(expss)

url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/us-weather-history/KPHL.csv"
weather_data <- read_csv(url)
```
#Section 3: Clean the data:
# Adding  a filter to the datframe weather_data
```{r, include=TRUE}
weather_PHL <-filter(weather_data,actual_mean_temp >= 19)
```
# renamed the column date to date_of_measurement
```{r, include=TRUE}
rename(weather_PHL,date_of_measurement = date)
```
# Selecting 4 coulumns from the dataframe
```{r, include=TRUE}
weather_PHL %>%
  select(1,2,3,4)

```
#Section 4: Characteristics of the data
We have data about `r nrow(weather_PHL)` rows and `r ncol(weather_PHL)`columns. The data is temperature measurements that were taken in the city of Philadelphia over the course of a 12 month period. The columns include the data that the temperature was recorded and the actual mean, min and max temperature. 


# Creating a table by seclecting 4 columns.
```{r, include=TRUE}
weather_PHL_TABLE <- weather_PHL %>%
  select(1,2,3,4)
weather_PHL_TABLE = apply_labels(weather_PHL, date = "date the temeprature was measured", actual_mean_temp ="actual mean temperature on the date" , actual_min_temp ="Actual minimum temeprature measured on the date", actual_max_temp = "Actual maximum temeperature measured on the date")
print(weather_PHL_TABLE)
```

#Section 5: Summary statistics - Selecting 3 columns from the dataframe. The columns that were used were the actual_mean_temp, actual_min_temp & actual_max_temp.
```{r, include=TRUE}
weather_PHL_SUM <- weather_data%>%
  select(2,3,4)
summary(weather_PHL_SUM)
```

